Predicting the Housing Market using \\ Linear Regression

### 2023-10-29 manuscript/Manuscript.tex
added a table describing the data

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{booktabs}

@@

% total of 545 entries, 13 columns (6 int and 7 str)
\begin{flushleft}
\begin{table}[h]
  \caption{Data Description}
  \label{tab:rv}
\centering
\begin{tabular}{llll}
  \toprule
Variable & Data Type & Instance & Purpose \\
  \midrule
price & Int & 13300000 & \(Y\) \\ 
area & Int & 7420 & \(X_{n}\) \\ 
bedrooms & Int & 4 & \(X_{n}\) \\ 
bathrooms & Int & 2 & \(X_{n}\) \\ 
stories & Int & 3 & \(X_{n}\) \\ 
mainroad & Str & yes, no & \(X_{n}\) \\
guestroom & Str & yes, no & \(X_{n}\) \\
basement & Str & yes, no & \(X_{n}\) \\
hotwaterheating & Str & yes, no & \(X_{n}\) \\
airconditioning & Str & yes, no & \(X_{n}\) \\
parking & Int & 2 & \(X_{n}\) \\
prefarea & Str & yes, no & \(X_{n}\) \\
furnishingstatus & Str & furnished, semi-furnished, unfurnished & \(X_{n}\) \\
   \bottomrule
\end{tabular}
\end{table}
\end{flushleft}
